What Variables Impact Wicket Production in the IPL

### 2024-12-13 paper/paper.qmd
fixed file names and citations

All cricket data is from the R [@citeR] package `cricketdata` [@cricketdata]. The data that was used is from the CRAN version of the package and not the Github [@github] developer tools version because the CRAN is more stable. The `cricketdata` [@cricketdata] package takes data from ESPN Cricinfo [@espncricinfo] and Cricsheet [@cricsheet]. While not stated by `cricketdata` [@cricketdata], based on the code the team behind the package are scrapping the HTML of ESPN Cricinfo and Cricsheet, As a result, anyone using the package must respect the rate limits set by these sites. Therefore, the data was first saved as CSV before performing any other data cleaning and analysis.

@@

The raw data set was acquired from the `cricketdata` [@cricketdata] R package. This data set had many contributors which can be seen through this [link](https://pkg.robjhyndman.com/cricketdata/), but the main developer is Rob Hyndman. The data set scraps the html from ESPN Cricinfo [@espncricinfo] and Cricsheet [@cricsheet]. These are two reputable organizations when it comes to cricket game data. Cricsheet [@cricsheet] is more so responsible for play by play cricket data, like giving the data for what happens for every ball in a game, whereas ESPN Cricinfo [@espncricinfo] is more responsible for general player career information and statistics.

@@

#### How complete is the data set?

@@

For play-by-play data the bowler, batsman, and teams involved in the play are present and so is general game information. Furthermore, the final outcome of the play, such as the number of runs, or if a wicket occurred are also given. Information about ball speed, distance, location, and fielding is not given. For player information, information about their country of citizenship, country of birth, batting style, bowling style, and batting order, and player role on a team are given. Potential missing observations with the player information are listed in @sec-complete-data set.

>>>>

All cricket data is from the R [@citeR] package `cricketdata` [@cricketdata]. The data that was used is from the CRAN version of the package and not the Github [@github] developer tools version because the CRAN is more stable. The `cricketdata` [@cricketdata] package takes data from ESPN Cricinfo [@espncricinfo] and Cricsheet [@cricsheet]. While not stated by `cricketdata` [@cricketdata], based on the code, the team behind the package are scrapping the HTML of ESPN Cricinfo [@espncricinfo] and downloading CSV data from Cricsheet [@cricsheet], As a result, anyone using the package must respect the rate limits set by these sites. Therefore, for this analysis the raw data was first saved as CSV before performing any other data cleaning and analysis.

@@

The raw data set was acquired from the `cricketdata` [@cricketdata] R package. This data set had many contributors which can be seen through this [link](https://pkg.robjhyndman.com/cricketdata/), but the main developer is Rob Hyndman. The data set scraps the html from ESPN Cricinfo [@espncricinfo] and downloads CSV data from Cricsheet [@cricsheet]. These are two reputable organizations when it comes to cricket game data. Cricsheet [@cricsheet] is more so responsible for play by play cricket data, like giving the data for what happens for every ball in a game, whereas ESPN Cricinfo [@espncricinfo] is more responsible for general player career information and statistics.

@@

#### How complete is the data set? {#sec-complete-data-set}

@@

For play-by-play data the bowler, batsman, and teams involved in the play are present and so is general game information. Furthermore, the final outcome of the play, such as the number of runs, or if a wicket occurred are also given. Information about ball speed, distance, location, and fielding is not given. For player information, information about their country of citizenship, country of birth, batting style, bowling style, and batting order, and player role on a team are given. Potential missing observations with the player information are listed in @sec-complete-data-set.
